Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2024-02-22 paper/main.tex
changed italics in one sentence

When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
question based on all other Quiz~1 questions, we observed an outcome consistent
with our null hypothesis: higher estimated knowledge at the embedding
coordinate of a held-out question was associated with a lower likelihood of
answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
\textit{not} provide useful information about participants' Quiz~1 performance
when we aggregated across all question content areas. We speculated that this
might either indicate that the knowledge estimates are uninformative in
general, or about Quiz~1 performance in particular. This would be expected, for
example, if participants were guessing about the answers to the Quiz~1
questions (prior to having watched either lecture). When we repeated this
analysis for Quizzes~2 and~3, we found that \textit{higher} estimated knowledge
for a given question predicted a greater likelihood of answering it correctly
(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
results suggest that our knowledge estimates reliably predict participants'
performance on individual held-out quiz questions, but only after participants
have received at least some training.

>>>>

When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
question based on all other Quiz~1 questions, we observed an outcome consistent
with our null hypothesis: higher estimated knowledge at the embedding
coordinate of a held-out question was associated with a lower likelihood of
answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
\textit{not} provide useful information about participants' Quiz~1 performance
when we aggregated across all question content areas. We speculated that this
might either indicate that the knowledge estimates are uninformative in
general, or about Quiz~1 performance in particular. This would be expected, for
example, if participants were guessing about the answers to the Quiz~1
questions (prior to having watched either lecture). When we repeated this
analysis for Quizzes~2 and~3, we found that higher estimated knowledge
for a given question predicted a \textit{greater} likelihood of answering it correctly
(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
results suggest that our knowledge estimates reliably predict participants'
performance on individual held-out quiz questions, but only after participants
have received at least some training.
